---
title: "空间广义线性混合效应模型及其应用"
subtitle: "Spatial Generalized Linear Mixed Models with Its Applications"
short-title: "空间广义线性混合效应模型"
author: "导师：李再兴 \\and 学生：黄湘云"
short-author: "李再兴 \\and 黄湘云"
date: '2015级硕士学位论文答辩'      # Month DD, YYYY (Main Slide)
short-date: '`r format(Sys.Date(), "%m/%d/%Y")`' # MM/DD/YYYY (Lower Right)
institute: "中国矿业大学（北京）理学院"
short-institute: "CUMTB"
department: "计算数学与统计系"                # Institute must be defined
license: "知识共享署名-非商业性使用-禁止演绎 4.0 国际许可协议"
section-titles: false                            # Provides slide headings
safe-columns: true                               # Enables special latex macros for columns.
output: 
   uiucthemes::beamer_illinois:
     latex_engine: xelatex
     citation_package: natbib
     toc: yes
header-includes:
   - \usepackage{ctex}
bibliography: refer.bib
biblio-style: apalike
biblio-title: 参考文献
link-citations: yes
colorlinks: yes
---


```{r setup, include=FALSE}
options(digits = 3)
knitr::opts_chunk$set(
  comment = "#>",
  echo = FALSE,
  collapse = TRUE,
  out.width = "70%",
  fig.align = 'center',
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold"
)
```

# 引言

### 研究背景

### 我做了什么

### 有什么意义

### 怎么做的

This is an R Markdown presentation [@bookdown2016CRC]. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.


### 模型假设

**Multiple prevalence surveys** 

Sample $n_{i}$ individuals, observe $Y_{i}$ positives, $i = 1, 2, \cdots, m$
$$Y_{i}\sim \mathrm{Bin}(n_{i},p_{i})$$
**Extra-binomial variation**

Sample $n_{i}$ individuals, observe $Y_{i}$ positives, $i = 1, 2, \cdots, m$
$$Y_{i}|d_{i},U_{i}\sim \mathrm{Bin}(n_{i},p_{i}) \quad 
\log[p_{i}/(1-p_{i})]=d_{i}'\beta+U_{i} \quad U_{i} \sim N(0,\tau^2)$$

### notations: Spatial Generalized Linear Mixed Models (SGLMM)

1. Latent spatially correlated process 
  - Stationary Gaussian Process: $S(x) \sim \mathrm{SGP}\{0,\sigma^2,\rho(u)\}$ 
  - correlation function: e.g. $\rho(u)=\exp(-|u|/\phi)$ 
2. Linear prediction (regression model)
  - $d(x)=$ covariates at location $x$
  - Linear prediction: $\eta(x)=d(x)'\beta + S(x)$ 
  - Link function: logit $p(x)=\log\{\eta(x)/[1-\eta(x)]\}$ 
3. Conditional distribution for positive proportion $Y_{i}/n_{i}$
  - $Y_{i}|S(\cdot) \sim \mathrm{Bin}(n_{i},p(x_{i}))$ (binomial sampling)

### 模拟实验

```{r simulation,fig.cap='精确方法与近似方法比较', out.width = '.6\\textwidth' }
knitr::include_graphics(path = 'figures/simulation.pdf')
```

### 还能怎么做

```{r pressure}
plot(pressure)
```

# Section title     
## Subsection title 

### Spatial data in R

- 动态文档 [@xie2015Dynamic;@bookdown2016CRC] 和 [@blogdown2017CRC]
- 统计图形 [@ggplot2016Springer]
- 空间统计 [@Venables2002Modern] 和 [@Bivand2013Applied]

*Edzer Pebesma* : useR! international R User conference

1. [Spatial data in R: simple features and future perspectives (2016)](https://channel9.msdn.com/Events/useR-international-R-User-conference/useR2016/Spatial-data-in-R-simple-features-and-future-perspectives) 
2. [Spatial data in R: new directions (2017)](https://channel9.msdn.com/Events/useR-international-R-User-conferences/useR-International-R-User-2017-Conference/Spatial-data-in-R-new-directions)
3. [Spatial data in R: new directions II (2017)](https://channel9.msdn.com/Events/useR-international-R-User-conferences/useR-International-R-User-2017-Conference/Spatial-data-in-R-new-directions-II) 

- UseR! tutorial <https://edzer.github.io/UseR2017/>

### \LaTeX

\begin{exampleblock}{Binomial Theorem}
\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  \label{eq:binom}
\end{equation} 
\end{exampleblock}

Hello Equation \ref{eq:binom}

#### Title for block box

**Unordered List**

- [University of Illinois at Urbana-Champaign (UIUC)](http://illinois.edu)
- [Department of Statistics](http://www.stat.illinois.edu/)
- [Illinois Informatics Institute](http://www.informatics.illinois.edu/) 


### Redux \LaTeX 

This theme supports special LaTeX macros `\beingcols` and `\endcols` that allows
for markdown to be blended with LaTeX without triggering the [`raw_tex`](http://pandoc.org/MANUAL.html#raw-tex) 
extension. To enable this feature, the `safe-columns` key in the YML head matter
must be set equal to `true`.

\begincols

\column{.49\linewidth}

- _Hello!_

\column{.49\linewidth}

1. **Goodbye!**

\endcols

## Code Example

### Code Embedding

```{r}
# Embedding code
x = 2
y = 3

x + y
```

Inline R code refering to variable in previous code chunk:

`r x`

